A GRASP algorithm for the concrete delivery problem.

### 2023-08-20 Article/article.tex
save article

\documentclass{article}
% \documentclass[review]{elsarticle}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage[algo2e,noend]{algorithm2e}
\usepackage[compatible,noend]{algpseudocode}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage[table,xcdraw]{xcolor}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage{bbding}
\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{tikz}
\usetikzlibrary{automata, topaths, calc, positioning, shapes, backgrounds, fit, matrix}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{datatool}
\usepackage{array}
\usepackage{pgfplotstable}
\pgfplotsset{width=7cm,compat=newest}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}
\usepackage{multirow}
\usepackage{float}
\usepackage[text={15cm,21cm},centering]{geometry}
\usepackage{setspace}
\usepackage{array}
\allowdisplaybreaks
\usepackage{lineno}
\usepackage{tkz-graph}
\usepackage{breqn}
\tikzset{
base/.style = {shape=rectangle, 
                      anchor=center,minimum size=5mm, 
                     align=center,
                     top color=white, ,inner sep=0ex,
                     minimum size=5mm
                     },
    LC11/.style =   {  base,   
                    text width=3em, 
                    bottom color=brown!100,
                    },
    UC11/.style = {     base,    
                    text width=5em, 
                    bottom color=brown!100,
                    align = right,
                },
    LC12/.style =   {  base,   
                    text width=1em, 
                    bottom color=orange!100,
                    },
    UC12/.style = {     base,    
                    text width=2.5em, 
                    bottom color=orange!100,
                },
    LC21/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=brown!100,
                    },
    UC21/.style = {     base,    
                    text width=3.5em, 
                    bottom color=brown!100,
                },
    LC22/.style =   {  base,   
                    text width=4em, 
                    bottom color=blue!100,
                    },
    UC22/.style = {     base,    
                    text width=7em, 
                    bottom color=blue!100,
                    align = left,
                },
    UC221/.style = {     base,    
                    text width=3.5em, 
                    bottom color=blue!100,
                    % color=blue!100,
                    outer xsep=0em,
                    % align = right,
                },
                UC231/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=blue!100,
                    },
    LC23/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=orange!100,
                    },
    UC23/.style = {     base,    
                    text width=2.em, 
                    bottom color=orange!100,
                },
  env/.style      = {base, font=\ttfamily\normalsize},
label/.style   = {base,font=\ttfamily\normalsize, text width = 8em, 
  inner sep=0em, rounded corners=1mm,bottom color=red!80,},
  dummy/.style    = {circle,draw}
}

@@

\begin{table}[htbp]
    \centering
    \caption{Performance of the GRASP heuristic on the CDP benchmark instances}
    \label{tab:cdp_instances}
    \resizebox{1\textwidth}{!}{
    \begin{tabular}{@{}cccccccccccc@{}}
    \toprule
     &  & \multicolumn{2}{c}{CP} & \multicolumn{2}{c}{MIP} & \multicolumn{2}{c}{SD-heuristic} & \multicolumn{2}{c}{Hybrid} & \multicolumn{2}{c}{GRASP} \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
     &  & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
    \multirow{2}{*}{Set A} & Avg & 4.2 & 197,012 & 7.3 & 13,405,798 & 9.1 & 23 & 7.0 & 100,765 & 5.7 & 13,186 \\ \cmidrule(l){2-10} \cmidrule(l){11-12} 
     & Opt & \multicolumn{2}{c}{40/64} & \multicolumn{2}{c}{37/64} & \multicolumn{2}{c}{30/64} & \multicolumn{2}{c}{35/64} & \multicolumn{2}{c}{35/64} \\ \cmidrule(l){3-10} \cmidrule(l){11-12} 
     \multirow{2}{*}{Set B} & Avg & 12.1 & 357,313 & - & - & 16.3 & 1,331 & - & - & 13.8 & 574,983\\ \cmidrule(l){2-10} \cmidrule(l){11-12} 
     & Opt & \multicolumn{2}{c}{55/128} & \multicolumn{2}{c}{-} & \multicolumn{2}{c}{40/128} & \multicolumn{2}{c}{-} & \multicolumn{2}{c}{44/128} \\ \bottomrule
    \end{tabular}
    }
\end{table}

@@

The computational results of our instances solved with the GRASP heuristic are summarized in the tables below. The stopping criterion is set to 20,000 iterations. The parameters used in our experiments are listed in Table~\ref*{tab:problem_parameters}.

\begin{table}[htpb]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
%    \resizebox*{\textwidth}{!}{
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Value} \\ \midrule
        Unloading duration ($\tau_c^u$) & 2 min$/m^3$ \\
        Cleaning duration ($\rho$) & 10 min \\
        Adjustment duration ($\alpha$) & 10 min \\
        Max travel time ($\Delta$) & 120 min \\
        Min working time ($M_T$) & 180 min \\
        Max working time ($N_T$) & 480 min \\
        Max overtime duration ($O_T$) & 120 min \\
        Max delay between two consecutive deliveries of the same order ($\gamma^1$) & 20 min \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min \\
    %    $\beta_1$ & 10000  \\
    %    $\beta_2$ & 10000  \\
    %    $\beta_3$ & 1000  \\
    %    $\beta_4$ & 100  \\
        \bottomrule
    \end{tabularx}
%    }
\end{table}

Table \ref*{tab:runtime} shows the percentage of concrete delivered by varying the execution times of the algorithm. For small instances, all requests are delivered in less than five minutes, while for medium and large instances, over 99\% of requests are delivered.  For these instances, it takes more than ten minutes to ensure complete delivery of all orders.

\begin{table}[htbp]
    \centering
    \caption{RMC delivered within different runtimes}
    \label{tab:runtime}
    \resizebox*{0.5\textwidth}{!}{
        \begin{tabular}{llcccc}
            \toprule
            &  &      \multicolumn{4}{c}{Runtime (min)} \\
            \cmidrule{3-6}
            & &      5   & 10  &  30  & 60  \\
            %  & {} &         &         &        &        \\
            \midrule
            \multirow{1}{*}{Small} & \% Load &  100.00 &  100.00 &  100.0 &  100.0 \\
                %   & \# instances &    8 &    8 &    8 &    8 \\
            \cmidrule{2-6}
                  \multirow{1}{*}{Medium} & \% Load &   99.86 &   99.86 &  100.0 &  100.0 \\
                %   & \# instances &   13 &   13 &   14 &   14 \\
                  \cmidrule{2-6}
                  \multirow{1}{*}{Large} & \% Load &   99.79 &   99.93 &  100.0 &  100.0 \\
                %   & \# instances &   12 &   13 &   14 &   14 \\
            \bottomrule
            \end{tabular} 
    }

Table \ref*{tab:results_grasp_ls} shows the detailed results for each instance. The runtime is set to 3600 seconds. The table reports the requirements of each instance, the components of the objective function, the number of drivers used, and the execution time in seconds.
%  the travel cost ($TC$), the penalties associated with unfulfilled orders ($PUO$), the sum of the first delivery delays ($FDD$) for each customer, the sum of the driver underutilization costs ($DUC$) and driver overtime costs ($DOC$).

All daily orders are served with our algorithm, using less drivers than the available fleet. For the small size instances, all first deliveries are timely, except for one instance. The sum of the driver underutilization costs ($DUC$) is high for medium and large instances. This indicates underutilization of the scheduled fleet. Some drivers are not scheduled at all or work very little. The sum of the driver overtime costs ($DOC$) is also high for these instances. This can be explained by the fact that the algorithm prefers to put certain drivers on overtime rather than use a driver who has to travel to another plant for a delivery, which would increase the travel cost ($TC$).

$FDD$ is the sum of the delays of the first deliveries. To get an idea of the actuel delay per customer, we report $mFDD$, which is the maximum delay for all first deliveries. This tells us that we have a maximum delay that varies between 0 and 12 minutes for small instances, 1 and 60 minutes for medium instances, and 50 to 60 minutes for large instances.

\begin{table}[htbp]

@@

    \label{tab:results_grasp_ls}
    \resizebox*{\textwidth}{!}{
        \begin{tabular}{llccccccccc}

@@

        &   &  Demand &  $TC$ & $PUO$&  $FDD$ & $mFDD$ &  $DUC$ &  $DOC$ &  \#Drivers &  Time \\
        & \multicolumn{1}{c}{Instance} &  (m$^3$)  &(min)  &  & (min) &(min) &(min)    & (min) & & (s)\\

@@

            \multirow{9}{*}{Small} & C\_13\_11\_12\_1 &          226.5 &     1243.55 &  0.0 &               0.00 &              0.00 &          66.01 &          0.00 &          13 &  3022.06 \\
                  & C\_13\_5\_8\_1 &          267.0 &      745.10 &  0.0 &               0.00 &              0.00 &           0.00 &          0.00 &          13 &  3027.39 \\
                  & C\_18\_6\_11\_2 &          333.5 &      753.26 &  0.0 &               0.00 &              0.00 &         653.78 &          0.00 &          17 &  3004.51 \\
                  & C\_15\_4\_7\_2 &          375.0 &     1013.11 &  0.0 &               0.00 &              0.00 &          56.79 &        244.61 &          15 &  3009.54 \\
                  & C\_19\_7\_8\_2 &          388.0 &     1714.74 &  0.0 &               0.00 &              0.00 &          97.56 &        283.83 &          19 &  3020.89 \\
                  & C\_29\_10\_14\_3 &          613.5 &     3724.29 &  0.0 &              12.41 &             12.41 &         246.04 &        454.51 &          28 &  3035.23 \\
                  & C\_31\_8\_11\_3 &          776.0 &     2297.20 &  0.0 &               0.00 &              0.00 &         627.37 &        539.96 &          30 &  3033.85 \\
                  & C\_35\_9\_10\_3 &          937.5 &     4077.20 &  0.0 &               0.00 &              0.00 &         720.00 &        866.98 &          31 &  3020.75 \\
                  \cmidrule{2-11}
                  \multirow{14}{*}{Medium} & C\_76\_40\_43\_6 &         1160.5 &     5715.53 &  0.0 &               1.00 &              1.00 &        3566.49 &        771.23 &          69 &  3021.92 \\
                  & C\_104\_42\_47\_8 &         1565.0 &     9114.62 &  0.0 &              23.00 &             16.24 &        4180.95 &        671.94 &          94 &  3047.99 \\
                  & C\_94\_63\_70\_7 &         1746.5 &    13888.90 &  0.0 &              19.86 &             12.40 &        1086.60 &       1477.76 &          94 &  3025.72 \\
                  & C\_116\_67\_78\_8 &         1839.5 &    13946.30 &  0.0 &              44.68 &              9.98 &        1578.90 &        639.28 &         116 &  3007.88 \\
                  & C\_116\_71\_82\_8 &         2060.0 &    12461.20 &  0.0 &              68.38 &             20.06 &        3119.66 &       1478.63 &         107 &  3028.24 \\
                  & C\_117\_57\_70\_6 &         2327.5 &    15066.80 &  0.0 &              83.79 &             16.44 &        1522.11 &       1892.64 &         117 &  3020.70 \\
                  & C\_137\_79\_83\_7 &         2425.0 &    18811.40 &  0.0 &             252.94 &             41.65 &        2193.63 &       1963.05 &         136 &  3025.83 \\
                  & C\_127\_66\_80\_8 &         2512.5 &    15177.80 &  0.0 &               2.00 &              2.00 &        1874.83 &        965.65 &         125 &  3007.70 \\
                  & C\_128\_68\_74\_7 &         2595.0 &    19133.50 &  0.0 &             251.77 &             54.40 &        1523.19 &       2924.28 &         128 &  3053.96 \\
                  & C\_136\_85\_97\_8 &         2673.0 &    16832.10 &  0.0 &             154.97 &             50.21 &        3507.40 &       1958.58 &         132 &  3028.15 \\
                  & C\_128\_78\_85\_8 &         2685.5 &    16927.30 &  0.0 &             202.26 &             50.12 &        1492.50 &       2794.21 &         128 &  3030.32 \\
                  & C\_131\_77\_85\_8 &         2893.5 &    17572.10 &  0.0 &             187.42 &             49.24 &        1803.22 &       1306.94 &         130 &  3040.74 \\
                  & C\_137\_89\_97\_7 &         2939.5 &    21934.10 &  0.0 &             697.18 &             59.10 &        1220.15 &       3038.33 &         137 &  3025.45 \\
                  & C\_133\_84\_98\_7 &         2971.0 &    22399.30 &  0.0 &             867.12 &             59.44 &         550.77 &       2887.51 &         133 &  3137.11 \\
                  \cmidrule{2-11}
                  \multirow{14}{*}{Large} & C\_132\_98\_109\_8 &         3078.5 &    23102.40 &  0.0 &             193.01 &             49.44 &         450.57 &       3931.83 &         132 &  3018.05 \\
                  & C\_129\_101\_119\_8 &         3229.0 &    18978.90 &  0.0 &             467.94 &             59.47 &        1084.78 &       2334.16 &         129 &  3179.81 \\
                  & C\_141\_114\_136\_8 &         3350.5 &    21760.00 &  0.0 &            1131.39 &             59.58 &        1284.13 &       2360.19 &         141 &  3056.56 \\
                  & C\_140\_114\_132\_8 &         3401.5 &    23259.00 &  0.0 &            1092.82 &             57.99 &         634.53 &       2705.26 &         140 &  3046.75 \\
                  & C\_143\_101\_123\_8 &         3437.5 &    24560.70 &  0.0 &             451.36 &             56.61 &        1663.43 &       4359.64 &         142 &  3039.02 \\
                  & C\_137\_112\_129\_8 &         3471.0 &    21526.10 &  0.0 &             252.62 &             58.09 &         624.87 &       3360.64 &         137 &  3018.76 \\
                  & C\_142\_114\_129\_8 &         3499.5 &    21991.50 &  0.0 &             898.10 &             55.22 &        1750.60 &       4943.03 &         142 &  3011.54 \\
                  & C\_149\_98\_122\_8 &         3513.0 &    20696.60 &  0.0 &             839.56 &             52.60 &        2465.87 &       2892.55 &         149 &  3072.58 \\
                  & C\_139\_98\_108\_8 &         3541.0 &    20550.10 &  0.0 &             566.69 &             57.49 &        1438.11 &       2910.97 &         139 &  3011.84 \\
                  & C\_144\_108\_122\_8 &         3670.5 &    23401.60 &  0.0 &             668.15 &             59.77 &        1438.60 &       3569.62 &         143 &  3056.51 \\
                  & C\_142\_92\_107\_8 &         3684.5 &    22700.20 &  0.0 &             147.42 &             48.31 &         899.82 &       3702.01 &         142 &  3019.52 \\
                  & C\_138\_114\_136\_8 &         3739.5 &    24670.70 &  0.0 &             750.04 &             55.88 &         518.63 &       5156.41 &         137 &  3021.26 \\
                  & C\_150\_127\_136\_8 &         3946.5 &    25822.20 &  0.0 &             742.75 &             57.10 &         899.92 &       5101.58 &         150 &  3060.79 \\
                  & C\_148\_112\_131\_8 &         3953.5 &    25455.30 &  0.0 &             868.81 &             49.15 &         500.68 &       3775.57 &         148 &  3005.96 \\

@@

We tried to reduce the maximum delay of the first delivery but found that some orders couldn't be fulfilled because of driver shifts and overtime constraints. We decided to remove these constraints and rerun our computation. We found that for small instances, the maximum delay dropped to zero, and for medium and large instances, it was reduced by almost 50\%. This suggests that when we input a good work schedule, our algorithm works effectively to ensure that all orders are filled and that delays for first deliveries and travel costs are minimized. In Table~\ref*{tab:lift_shift_constraints}, we can see that the average travel time decreases for all instances except the large ones. That's because the goals of minimizing travel cost and not delaying the first delivery are sometimes in conflict: to ensure that the first delivery is not late, drivers assigned to one plant often have to travel to another. And since all plants are used in large cases, this can increase travel times.

>>>>

\documentclass{article}
% \documentclass[review]{elsarticle}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage[algo2e,noend]{algorithm2e}
\usepackage[compatible,noend]{algpseudocode}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage[table,xcdraw]{xcolor}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage{bbding}
\usepackage[english]{babel}
\usepackage{adjustbox}
\usepackage{tikz}
\usepackage{subcaption}
\usetikzlibrary{automata, topaths, calc, positioning, shapes, backgrounds, fit, matrix}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{datatool}
\usepackage{array}
\usepackage{pgfplotstable}
\pgfplotsset{width=7cm,compat=newest}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage{capt-of}
\usepackage{multirow}
\usepackage{float}
\usepackage[text={15cm,21cm},centering]{geometry}
\usepackage{setspace}
\usepackage{array}
\allowdisplaybreaks
\usepackage{lineno}
\usepackage{tkz-graph}
\usepackage{breqn}

\tikzset{
base/.style = {shape=rectangle, 
                      anchor=center,minimum size=5mm, 
                     align=center,
                     top color=white, ,inner sep=0ex,
                     minimum size=5mm
                     },
    LC11/.style =   {  base,   
                    text width=3em, 
                    bottom color=brown!100,
                    },
    UC11/.style = {     base,    
                    text width=5em, 
                    bottom color=brown!100,
                    align = right,
                },
    LC12/.style =   {  base,   
                    text width=1em, 
                    bottom color=orange!100,
                    },
    UC12/.style = {     base,    
                    text width=2.5em, 
                    bottom color=orange!100,
                },
    LC21/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=brown!100,
                    },
    UC21/.style = {     base,    
                    text width=3.5em, 
                    bottom color=brown!100,
                },
    LC22/.style =   {  base,   
                    text width=4em, 
                    bottom color=blue!100,
                    },
    UC22/.style = {     base,    
                    text width=7em, 
                    bottom color=blue!100,
                    align = left,
                },
    UC221/.style = {     base,    
                    text width=3.5em, 
                    bottom color=blue!100,
                    % color=blue!100,
                    outer xsep=0em,
                    % align = right,
                },
                UC231/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=blue!100,
                    },
    LC23/.style =   {  base,   
                    text width=1.5em, 
                    bottom color=orange!100,
                    },
    UC23/.style = {     base,    
                    text width=2.em, 
                    bottom color=orange!100,
                },
  env/.style      = {base, font=\ttfamily\normalsize},
label/.style   = {base,font=\ttfamily\normalsize, text width = 8em, 
  inner sep=0em, rounded corners=1mm,bottom color=red!80,},
  dummy/.style    = {circle,draw}
}
\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}

@@

\begin{table}[htbp]
    \centering
    \caption{Performance of the GRASP heuristic on the CDP benchmark instances}
    \label{tab:cdp_instances}
    \scriptsize
    \resizebox{1\textwidth}{!}{
        \begin{tabular}{@{}cccccccccccc@{}}
            \toprule
                                   &     & \multicolumn{2}{c}{CP}     & \multicolumn{2}{c}{MIP}   & \multicolumn{2}{c}{SD-heuristic} & \multicolumn{2}{c}{Hybrid} & \multicolumn{2}{c}{GRASP}                                                            \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
                                   &     & Gap (\%)                   & Time (ms)                 & Gap (\%)                         & Time (ms)                  & Gap (\%)                   & Time (ms) & Gap (\%) & Time (ms) & Gap (\%) & Time (ms) \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
            \multirow{2}{*}{Set A} & Avg & 4.2                        & 197,012                   & 7.3                              & 13,405,798                 & 9.1                        & 23        & 7.0      & 100,765   & 5.7      & 13,186    \\ \cmidrule(l){2-10} \cmidrule(l){11-12}
                                   & Opt & \multicolumn{2}{c}{40/64}  & \multicolumn{2}{c}{37/64} & \multicolumn{2}{c}{30/64}        & \multicolumn{2}{c}{35/64}  & \multicolumn{2}{c}{35/64}                                                            \\ \cmidrule(l){3-10} \cmidrule(l){11-12}
            \multirow{2}{*}{Set B} & Avg & 12.1                       & 357,313                   & -                                & -                          & 16.3                       & 1,331     & -        & -         & 13.8     & 574,983   \\ \cmidrule(l){2-10} \cmidrule(l){11-12}
                                   & Opt & \multicolumn{2}{c}{55/128} & \multicolumn{2}{c}{-}     & \multicolumn{2}{c}{40/128}       & \multicolumn{2}{c}{-}      & \multicolumn{2}{c}{44/128}                                                           \\ \bottomrule
        \end{tabular}
    }
\end{table}

@@

The computational results of our instances solved with the GRASP heuristic are summarized in the tables below. %The stopping criteria are set to 20,000 iterations or 3600 seconds of running time (unless otherwise specified).
The parameters used in our experiments are listed in Table~\ref*{tab:problem_parameters}.

\begin{table}[hbt]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
    \small
    %    \resizebox*{\textwidth}{!}{
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter}                                                 & \multicolumn{1}{c}{Value} \\ \midrule
        Unloading duration ($\tau_c^u$)                                               & 2 min$/m^3$               \\
        Cleaning duration ($\rho$)                                                    & 10 min                    \\
        Adjustment duration ($\alpha$)                                                & 10 min                    \\
        Max travel time ($\Delta$)                                                    & 120 min                   \\
        Min working time ($M_T$)                                                      & 180 min                   \\
        Max working time ($N_T$)                                                      & 480 min                   \\
        Max overtime duration ($O_T$)                                                 & 120 min                   \\
        Max delay between two consecutive deliveries of the same order $\gamma^1$)   & 20 min                    \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min                    \\
        Penalty of unfulfilled orders ($\beta_1$)                                     & 10,0000                   \\
        Penalty of first delivery delay ($\beta_2$)                                   & 1,0000                    \\
        Penalty for driver underutilization  ($\beta_3$)                              & 30                        \\
        Driver overtime penalty $ (\beta_4$)                                          & 20                        \\
        \bottomrule
    \end{tabularx}
    %    }
\end{table}
%  the travel cost ($TC$), the penalties associated with unfulfilled orders ($PUO$), the sum of the first delivery delays ($FDD$) for each customer, the sum of the driver underutilization costs ($DUC$) and driver overtime costs ($DOC$).
The table \ref*{tab:all_instances} contains the detailed results for all instances with a stop criterion of 3600 seconds. The table shows the demand of each instance, the average and the best values of the objective function when solving each instance five times. All daily orders are served by our algorithm within these five replications. On average, five instances require multiple runs of the algorithm to successfully serve all customers, as shown in column $UQ$, which is the undelivered quantity. The sum of the driver underutilization costs ($DUC$) is high for medium and large instances. This indicates the underutilization of the scheduled fleet. Some drivers are not scheduled at all or work very little. The sum of driver overtime costs ($DOC$) is also high for these instances. This can be explained by the fact that the algorithm prefers to put certain drivers on overtime rather than use a driver who has to travel to another plant for a delivery, which would increase the travel costs ($TC$).

$FDD$ is the sum of the delays of the first deliveries.  For the small instances, all but one of the first deliveries are on time. For the other instances, there is at least one customer with a late first delivery.
To get an idea of the actual delay per customer, we report $mFDD$, which is the maximum delay of all first deliveries. This tells us that we have a maximum delay that varies between 0 and 19 minutes for small instances, 3.5 and 60 minutes for medium instances, and 24 to 60 minutes for large instances.

\begin{table}[!ht]
    \centering

@@

    \label{tab:all_instances}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{llccccccccccccc}

@@

    &                 &          & \multicolumn{6}{c}{Avg} & \multicolumn{6}{c}{Best}   \\
    \cmidrule(l){4-9} \cmidrule(l){10-15}
    &  & Demand   & $UQ$   & $TC$  & $FDD$    & $DUC$    & $DOC$    & \multirow[c]{2}{*}{Z} & $TC$      & $FDD$    & $mFDD$  & $DUC$    & $DOC$    & \multirow[c]{2}{*}{Z} \\
        & & ($m^3$)  & ($m^3$) & (min)  & (min)    & (min)    & (min)    &     & (min)     & (min)    & (min) & (min)   &(min)& \\

@@

        \multirow[c]{8}{*}{Small} & C_13_11_12_1 & 226.5 & 0.0 & 1,243.5 & 0.0 & 37.7 & 0.0 & 2,373.9 & 1,243.5 & 0.0 & 0.0 & 0.0 & 0.0 & 1,243.5 \\
        & C_13_5_8_1 & 267.0 & 0.0 & 745.1 & 0.0 & 0.0 & 0.0 & 745.1 & 745.1 & 0.0 & 0.0 & 0.0 & 0.0 & 745.1 \\
        & C_18_6_11_2 & 333.5 & 0.0 & 753.3 & 0.0 & 194.7 & 0.0 & 6,593.7 & 753.3 & 0.0 & 0.0 & 125.3 & 0.0 & 4,513.2 \\
        & C_15_4_7_2 & 375.0 & 0.0 & 1,014.9 & 0.0 & 132.8 & 291.6 & 10,830.8 & 1,014.2 & 0.0 & 0.0 & 172.1 & 76.1 & 7,700.1 \\
        & C_19_7_8_2 & 388.0 & 0.0 & 1,765.5 & 0.0 & 314.8 & 150.9 & 14,225.6 & 1,745.8 & 0.0 & 0.0 & 224.5 & 87.9 & 10,237.1 \\
        & C_29_10_14_3 & 613.5 & 0.0 & 3,742.0 & 48.6 & 211.0 & 735.6 & 73,392.7 & 3,628.8 & 49.2 & 18.8 & 112.9 & 547.2 & 67,145.2 \\
        & C_31_8_11_3 & 776.0 & 0.0 & 2,330.6 & 0.0 & 781.6 & 656.5 & 38,909.6 & 2,297.2 & 0.0 & 0.0 & 606.7 & 567.0 & 31,836.1 \\
        & C_35_9_10_3 & 937.5 & 0.0 & 4,175.3 & 0.0 & 341.8 & 1,329.5 & 41,021.0 & 4,174.4 & 0.0 & 0.0 & 221.7 & 1,161.6 & 34,057.0 \\
        \cmidrule(l){1-15}
        \multirow[c]{14}{*}{Medium} & C_76_40_43_6 & 1,160.5 & 0.0 & 6,311.6 & 17.2 & 3,014.6 & 706.0 & 128,106.4 & 5,967.0 & 6.2 & 3.5 & 2,961.6 & 644.4 & 113,884.7 \\
        & C_104_42_47_8 & 1,565.0 & 0.0 & 9,358.2 & 34.1 & 3,890.1 & 679.0 & 173,754.5 & 9,777.5 & 32.0 & 13.0 & 2,830.0 & 240.6 & 131,507.6 \\
        & C_94_63_70_7 & 1,746.5 & 0.0 & 14,369.1 & 90.2 & 1,353.9 & 1,391.4 & 173,007.0 & 14,428.7 & 78.9 & 19.3 & 1,147.9 & 1,464.3 & 157,038.1 \\
        & C_116_67_78_8 & 1,839.5 & 0.0 & 13,602.9 & 67.9 & 2,419.4 & 857.3 & 171,229.1 & 13,871.9 & 67.2 & 33.2 & 2,347.7 & 523.3 & 162,021.5 \\
        & C_116_71_82_8 & 2,060.0 & 0.0 & 12,678.2 & 158.6 & 1,991.3 & 1,125.8 & 253,575.1 & 12,089.7 & 147.7 & 27.2 & 1,966.0 & 922.7 & 237,183.6 \\
        & C_117_57_70_6 & 2,327.5 & 0.0 & 15,495.0 & 142.4 & 1,388.6 & 1,680.5 & 233,181.4 & 15,153.3 & 114.2 & 22.2 & 1,823.7 & 1,671.5 & 217,448.3 \\
        & C_137_79_83_7 & 2,425.0 & 0.0 & 18,960.4 & 375.8 & 2,124.7 & 1,857.9 & 495,614.5 & 18,360.3 & 335.1 & 34.2 & 2,552.7 & 1,794.2 & 465,977.3 \\
        & C_127_66_80_8 & 2,512.5 & 0.0 & 16,033.3 & 10.4 & 1,579.6 & 1,552.1 & 104,879.1 & 17,599.1 & 14.4 & 5.0 & 1,046.3 & 1,242.3 & 88,203.5 \\
        & C_128_68_74_7 & 2,595.0 & 0.0 & 19,774.4 & 361.6 & 944.6 & 2,616.7 & 461,998.2 & 18,728.8 & 191.0 & 42.5 & 1,418.8 & 2,841.2 & 309,116.8 \\
        & C_136_85_97_8 & 2,673.0 & 0.0 & 18,223.6 & 188.5 & 2,134.5 & 2,352.2 & 317,811.4 & 18,894.6 & 137.4 & 48.6 & 1,155.6 & 2,137.0 & 233,669.0 \\
        & C_128_78_85_8 & 2,685.5 & 0.0 & 18,463.9 & 305.8 & 1,277.3 & 3,157.0 & 425,759.3 & 18,041.6 & 192.4 & 35.7 & 1,374.3 & 3,234.2 & 316,314.1 \\
        & C_131_77_85_8 & 2,893.5 & 0.0 & 18,003.0 & 212.6 & 1,248.7 & 1,716.1 & 302,370.4 & 18,063.0 & 200.2 & 43.2 & 780.7 & 1,539.1 & 272,509.6 \\
        & C_137_89_97_7 & 2,939.5 & 0.0 & 23,293.0 & 636.0 & 849.9 & 3,523.9 & 755,280.5 & 22,038.1 & 438.3 & 58.6 & 849.8 & 3,461.1 & 555,029.1 \\
        & C_133_84_98_7 & 2,971.0 & 18.7 & 22,000.0 & 1,157.6 & 805.4 & 2,291.4 & 1,249,585.1 & 20,992.6 & 1,061.2 & 59.4 & 546.1 & 2,742.5 & 1,153,396.1 \\
        \cmidrule(l){1-15}
        \multirow[c]{14}{*}{Large} & C_132_98_109_8 & 3,078.5 & 0.0 & 23,469.1 & 247.4 & 548.7 & 4,162.3 & 370,622.5 & 23,425.8 & 160.9 & 29.4 & 493.2 & 4,426.1 & 287,683.7 \\
        & C_129_101_119_8 & 3,229.0 & 0.0 & 19,051.7 & 269.0 & 1,232.1 & 3,820.4 & 401,387.9 & 19,453.3 & 166.7 & 35.8 & 1,138.1 & 4,719.6 & 314,728.3 \\
        & C_141_114_136_8 & 3,350.5 & 8.7 & 21,505.6 & 1,127.2 & 1,422.7 & 2,339.2 & 1,238,202.0 & 21,863.2 & 943.9 & 55.4 & 1,177.0 & 2,513.4 & 1,051,386.9 \\
        & C_140_114_132_8 & 3,401.5 & 0.0 & 23,938.4 & 1,055.1 & 910.2 & 3,269.1 & 1,171,715.1 & 23,969.7 & 988.5 & 54.4 & 981.3 & 3,253.1 & 1,107,019.4 \\
        & C_143_101_123_8 & 3,437.5 & 0.0 & 25,711.0 & 352.2 & 903.0 & 4,085.1 & 486,755.0 & 26,284.9 & 335.5 & 43.5 & 566.1 & 3,913.0 & 457,007.0 \\
        & C_137_112_129_8 & 3,471.0 & 0.0 & 22,562.4 & 340.8 & 402.4 & 3,371.1 & 442,869.1 & 22,338.3 & 275.1 & 45.6 & 375.2 & 3,819.8 & 385,076.1 \\
        & C_142_114_129_8 & 3,499.5 & 0.0 & 22,478.3 & 801.0 & 1,294.8 & 4,168.2 & 945,633.4 & 22,387.6 & 654.6 & 55.3 & 1,090.4 & 4,472.6 & 799,184.0 \\
        & C_149_98_122_8 & 3,513.0 & 3.0 & 20,767.5 & 778.4 & 2,236.9 & 2,852.2 & 923,357.9 & 21,224.7 & 684.5 & 51.1 & 2,267.6 & 3,046.6 & 834,708.6 \\
        & C_139_98_108_8 & 3,541.0 & 0.0 & 21,613.4 & 661.0 & 852.3 & 3,716.2 & 782,546.8 & 22,043.2 & 522.3 & 51.6 & 482.8 & 3,648.5 & 631,819.8 \\
        & C_144_108_122_8 & 3,670.5 & 0.0 & 24,738.3 & 746.0 & 664.9 & 3,465.8 & 860,025.7 & 25,806.9 & 675.4 & 50.4 & 548.5 & 3,209.2 & 781,866.1 \\
        & C_142_92_107_8 & 3,684.5 & 0.0 & 24,553.3 & 298.6 & 644.2 & 4,423.6 & 431,001.0 & 23,586.4 & 182.6 & 24.0 & 803.0 & 4,396.5 & 318,243.2 \\
        & C_138_114_136_8 & 3,739.5 & 0.0 & 25,366.9 & 791.5 & 668.6 & 5,501.8 & 946,993.9 & 23,639.0 & 600.4 & 55.2 & 1,230.8 & 5,314.0 & 767,223.0 \\
        & C_150_127_136_8 & 3,946.5 & 0.0 & 25,785.2 & 613.8 & 629.1 & 4,686.4 & 752,189.6 & 27,332.9 & 507.3 & 57.1 & 250.3 & 5,295.7 & 648,057.4 \\
        & C_148_112_131_8 & 3,953.5 & 6.9 & 26,231.2 & 1,002.0 & 517.8 & 3,467.4 & 1,113,149.3 & 25,559.2 & 886.9 & 56.0 & 559.3 & 4,213.2 & 1,013,500.2 \\

@@

Table \ref{tab:runtime} shows the percentage of concrete delivered by varying the execution times of the algorithm. For small instances, all requests are delivered in less than a minute, while for medium and large instances, over 99\% of requests are delivered.  For these instances, it takes more than ten minutes to ensure complete delivery of all orders.
